Papers

### 2025-09-25 papers.qmd
update

@@

-   Brand, C. O., Brady, D., & Stafford, T. (in press). [The Ideological Turing Test: a behavioural measure of open-mindedness and perspective-taking](https://psyarxiv.com/2e9wn). *Cognitive Science*. https://doi.org/10.31234/osf.io/2e9wn

@@

-   Stafford, T. (2018). [Female chess players outperform expectations when playing men](http://journals.sagepub.com/doi/10.1177/0956797617736887). Psychological Science, 29(3), 429-436. (Preprint).

>>>>

-    Panagiotidi, M., Zavlis, O., Jones, M., & Stafford, T. (2024). [The three-dimensional community structure of attention-deficit hyperactivity disorder (ADHD) traits captured by the Adult ADHD Self-Report Scale: An exploratory graph analysis](https://onlinelibrary.wiley.com/doi/full/10.1002/mpr.1997). International Journal of Methods in Psychiatric Research, e1997. <https://doi.org/10.1002/mpr.1997> [[preprint](https://psyarxiv.com/sakn9), [Data/code](https://osf.io/sd6f5/)]

-   Stafford, T., and Vaci, N. (2022). [Maximizing the potential of digital games for understanding skill acquisition](https://doi.org/10.1177/09637214211057841). Current Directions in Psychological Science, 31(1), 49-55.  <https://doi.org/10.1177/09637214211057841> [[web/mobile version](https://journals.sagepub.com/doi/full/10.1177/09637214211057841), [Code](https://osf.io/fvm8s/files/osfstorage)]

@@

-   Brand, C. O., Brady, D., & Stafford, T. (in press). [The Ideological Turing Test: a behavioural measure of open-mindedness and perspective-taking](https://psyarxiv.com/2e9wn). *Cognitive Science*. [Preprint](https://doi.org/10.31234/osf.io/2e9wn), [Data/Code](https://doi.org/10.5281/zenodo.16872578).

@@

-   Stafford, T. (2018). [Female chess players outperform expectations when playing men](http://journals.sagepub.com/doi/10.1177/0956797617736887). Psychological Science, 29(3), 429-436. https://doi.org/10.1177/095679761773688 [Preprint](https://osf.io/preprints/psyarxiv/bpy3t), [Code/Data](https://osf.io/aeksv).
